%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\def\spaceBetween{-1cm}
\def\spaceAfter{0.1cm}

% \cvsection{Publication \& Conferences}
\cvsection{Publication}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvpublication}
\vspace{-2mm}
%---------------------------------------------------------
    \cvpub
        {\begin{cvitems}
            \item {A. B. Rajeoni, B. Pederson, \textbf{A. Firooz}, et al. "TransONet: Automatic Segmentation of Vasculature in Computed Tomographic Angiograms Using Deep Learning." in 2023 International Conference on Computational Science and Computational Intelligence (CSCI), 2023, \href{https://doi.org/10.48550/arXiv.2311.10328}{doi.org/10.48550/arXiv.2311.10328}.}
        \end{cvitems}}
    {}
    % ---------------------------------------------------------
    \cvpub
        {\begin{cvitems}
            \item {B. K. Austin, \textbf{A. Firooz,} H. Valafar, and A. V. Blenda, “An Updated Overview of Existing Cancer Databases and Identified Needs", Biology, vol. 12, no. 8, 2023.}
        \end{cvitems}}
        {}
    %---------------------------------------------------------
    \cvpub
        {\begin{cvitems}
            \item {\textbf{A. Firooz,} A. T. Funkhouser, J. C. Martin, W. J. Edenfield, H. Valafar, and A. V. Blenda, “Comprehensive and User-Analytics-Friendly Cancer Patient Database for Physicians and Researchers", in 2022 International Conference on Computational Science and Computational Intelligence (CSCI), 2022, pp. 1615–1621.}
        \end{cvitems}}
        {}
    %---------------------------------------------------------
    \cvpub
        {\begin{cvitems}
            \item {\textbf{A. Firooz,} A. T. Funkhouser, J. C. Martin, W. J. Edenfield, H. Valafar, and A. V. Blenda, “Analysis of cancer patients’ molecular and clinical data using artificial intelligence and machine learning approaches", Cancer Research, vol. 83, no. 7 Supplement, pp. 5425–5425, 04 2023.}
        \end{cvitems}}
        {}
    % ---------------------------------------------------------
    \cvpub
        {\begin{cvitems}
            \item {\textbf{A. Firooz,} S. M. Noblitt, J. Martin, W. J. Edenfield, A. Blenda, and H. Valafar, “Application of machine learning in predicting breast cancer patient outcome," BMC Proceedings, vol. 17, no. 19, pp. O11, 2023. \href{https://doi.org/10.1186/s12919-023-00281-y}{doi.org/10.1186/s12919-023-00281-y}}
        \end{cvitems}}
    {}
    % ---------------------------------------------------------
    % \vspace{2mm}
    % \cvpub
    %     {\begin{cvitems}
    %         \item {}
    %     \end{cvitems}}
    %     {\hspace{-6mm}Conferences}
    % ---------------------------------------------------------
    % \cvpub
    %     {\begin{cvitems}
    %         \item {}
    %     \end{cvitems}}
    % {}
%---------------------------------------------------------
\end{cvpublication}
