%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Experience}
\vspace*{-0.2cm}

%===============================================================================
%	CONTENT
%===============================================================================
% \cvsubsection{Computer Science and Engineering}
\begin{cventries}

%---------------------------------------------------------

\cventry
    {Prisma Health Cancer Institute \hspace{0.1cm} \& \hspace{0.1cm} School of Medicine Greenville}
    {Graduate Researcher Assistant}
    {\ifdefstring{\solution}{phd}{Jul 2022 -- Dec 2024}{Jul 2022 -- Dec 2024}}
    {Remote, SC, US}
    {
        \begin{cvitemsfree}
            \item{Collaborated with an \textbf{8-member cross-functional team} (physicians, biologists, and computer scientists) delivering data-driven insights.}
            % 
            \item{Implemented a SQL database with \textbf{over 10K clinical records} using ORM \& migration tools, ensuring reliability and high-performance.} % using SQLAlchemy ORM
            % 
            \item{Developed a modular \textbf{Python ETL pipeline} to parse, clean, validate, and ingest clinical datasets, improving data reliability.}
            % data enrichment
            % 
            \item{Conducted comprehensive \textbf{ML/DL experiments} to classify patient responses across 65 drug combinations, addressing anomalies, class imbalance, and missingness, while using a \textbf{4-metric evaluation system.}}
            % 
            \item{Utilized \textbf{XAI (SHAP)} to provide clinicians with transparent model explanations, enabling informed decisions.}
        \end{cvitemsfree}
    }

\vspace*{0.2cm}
%---------------------------------------------------------

\cventry
    {University of South Carolina}
    {Graduate Research Assistant}
    {Jan 2022 -- Dec 2024}
    {Columbia, SC, US}
    {
        \begin{cvitemsfree}
            \item{Processed \textbf{over 6.9 billion} mass spectrometry data points in parallel from 78 raw instrument files, used async ingestion to store results in MySQL, significantly reducing pipeline latency.}
            % 
            \item{Built deep CNNs and ResNet for binary classification of cancerous tissue using the MS data.}
            % 
            \item{Co-developed TransONet: a \textbf{ResNet-Transformer-UNet} hybrid approach, achieving 93.5\% Dice score for aortic segmentation in CT scans.}
        \end{cvitemsfree}
    }

\vspace*{0.2cm}
%---------------------------------------------------------

\cventry
    {}
    {Selected Projects}
    {}
    {}
    {
        \begin{cvitemsfree}
            \item{\textbf{Coordinated a 5-member team} to build a cloud-native certificate management system using \textbf{Azure} (SQL DB, Blob Storage, Service Bus, Logic Apps, Functions, Data Factory) and \textbf{Azure DevOps.} Used .NET Core 7, EF Core, and React; integrated CI/CD and serverless architecture.}
            % Implemented features including data integration from external feeds, CRUD operations with notifications, dashboards, user profiles, and certificate catalogs.
            %
            \item{Applied dimension reduction techniques to \textbf{over 77K small molecule chemical descriptors} for unsupervised clustering. Trained an XGBoost model with optimized hyperparameters for retention time prediction, achieving RMSE \approx \space 8.}
            %
            \item{prototyped a RAG-based chatbot for USC Hackathon using \textbf{LangChain,} LangSmith, and \textbf{MongoDB} Atlas Vector DB.}
            %
            \item{Implemented a \textbf{domain-specific RAG-based agent} for question answering over research papers, covering prompt versioning, document reasoning, vector stores, embeddings semantic similarity, and LLM as a judge.}
            %
            \item{Designed and deployed a \textbf{Hybrid GraphRAG Agent} using \textbf{LangGraph,} LangSmith, Neo4j, and vision LLMs. Extracted structured data from PDFs (graphs, tables, images) using VLM; implemented advanced \textbf{semantic similarity chunking} and document ingestion with progress tracking.}
            %
            \item{Developed and deployed a \textbf{semantic segmentation} model on \textbf{AWS SageMaker,} trained to segment images into foreground, background, and transition classes.}
            % 
            % \item{Completed a project-based PyTorch course focused on computer vision. Implemented binary and multi-class classification, object detection with bounding boxes, and semantic/instance/panoptic segmentation. Developed GANs for image synthesis and evaluated model performance.}
            % 
            % \item{Studied the lifecycle of LLMs in a course on Generative AI, covering architecture, fine-tuning, evaluation metrics, and deployment. Applied scaling laws and constraint-aware optimization strategies in LLM projects.}
            % 
            % \item{Attended a 5-day Gen AI intensive program by Google covering: foundational models and prompt engineering, embeddings and vector search, generative agents, domain-specific LLMs (e.g., Med-PaLM), and MLOps for generative AI. Hands-on coding throughout using Gemini and Vertex AI.}
            % 
            % \item{Implemented Vision Transformer (ViT) models in PyTorch Lightning for image classification tasks.}
            % 
            % \item{Fine-tuned Hugging Face ALBERT on TripAdvisor sentiment analysis; handled tokenization, training, and evaluation.}
        \end{cvitemsfree}
    }

\vspace*{0.2cm}
%---------------------------------------------------------

\ifdefstring{\solution}{mschem}{
    \input{resume/experience-chem.tex}
}{}

%---------------------------------------------------------

% \cventry
    % {Finance Investor} % Job title
    % {} % Organization
    % {2015 - 2020} % Date(s)
    % {} % Location
    % {
    %     \SubItem{\vspace{-0.4cm}Experienced a 150\% growth rate, in 5 years, as a result of utilizing money management techniques and applying both fundamental and technical analysis to Iranian stocks.
    %     }
    % }

%---------------------------------------------------------
\end{cventries}